Digital Analysis of Paintings

### 2014-05-07 paper.tex
Van Gogh -> van Gogh.

In the experimental results this paper provides, the latter is achieved by a
study of another of Van Gogh's works from the same time.

@@

With promising results shown from this experimentation, attention was turned to
a norm for painting analysis: Van Gogh. Rather than consider the global state
of the canvas, each image was split into smaller sections for the analysis, as
paintings very rarely have the same texture globally.

@@

The data sets used are relatively small and, although they increase the
knowledge by taking multiple patches from the Van Gogh paintings, but for the
results they show only individual paintings are considered. One could easily
question the validity of their results based on this.

@@

The results on 117 high-resolution grayscale Van Gogh paintings show that most
of the non-Van Gogh paintings appear on the peripheries of the visualised
two-dimensional graph, apart from two specific forgeries: the Wacker forgery
which had fooled experts for many years, but can successfully be found by
looking at global features. The other, created by Gaugin, may remain undetected
for the same reason.

Visualisation of dated Van Gogh work does show some difference between the two
time periods considered, but not enough to cluster or classify upon with any
degree of accuracy.

@@

Results for the dating challenge, 66 Van Gogh paintings were used with the goal
of dating three test images which cannot be easily dated by art historians.
Training was performed on the set of paintings using 10-fold cross-validation
using several different classifiers. The best classifier; random forest; had a
generalisation performance of 73.7\% and the results from the three test images
aligned with the conclusions of the art historians, but this is somewhat
conjecture as the dates aren't officially known.

@@

This was also to applied to a painting by Pietro di Cristoforo Vannucci
(Perugino) which is disputed by art historians to have been produced by more
than a single artists, which, during the Renaissance was common amoungst the
great works.

@@

All experimental results were gathered from a data set containing 101 paintings
in the style of Van Gogh. 82 of which are believed to be true Van Gogh works,
13 which are currently in dispute and 6 which are known imitations. All of
these paintings are scaled using the same technique to be equivalent sizes.

The approach for using Penn State was to gather several unquestionably Van Gogh
paintings which are representative of his style (exemplar images) as a training
set. By not including negative examples in the training set the resulting
classifier is more stringent.

>>>>

In the experimental results this paper provides, the latter is achieved by a
study of another of van Gogh's works from the same time.

@@

With promising results shown from this experimentation, attention was turned to
a norm for painting analysis: van Gogh. Rather than consider the global state
of the canvas, each image was split into smaller sections for the analysis, as
paintings very rarely have the same texture globally.

@@

The data sets used are relatively small and, although they increase the
knowledge by taking multiple patches from the van Gogh paintings, but for the
results they show only individual paintings are considered. One could easily
question the validity of their results based on this.

@@

The results on 117 high-resolution grayscale van Gogh paintings show that most
of the non-van Gogh paintings appear on the peripheries of the visualised
two-dimensional graph, apart from two specific forgeries: the Wacker forgery
which had fooled experts for many years, but can successfully be found by
looking at global features. The other, created by Gaugin, may remain undetected
for the same reason.

Visualisation of dated van Gogh work does show some difference between the two
time periods considered, but not enough to cluster or classify upon with any
degree of accuracy.

@@

Results for the dating challenge, 66 van Gogh paintings were used with the goal
of dating three test images which cannot be easily dated by art historians.
Training was performed on the set of paintings using 10-fold cross-validation
using several different classifiers. The best classifier; random forest; had a
generalisation performance of 73.7\% and the results from the three test images
aligned with the conclusions of the art historians, but this is somewhat
conjecture as the dates aren't officially known.

@@

This was also to applied to a painting by Pietro di Cristoforo vannucci
(Perugino) which is disputed by art historians to have been produced by more
than a single artists, which, during the Renaissance was common amoungst the
great works.

@@

All experimental results were gathered from a data set containing 101 paintings
in the style of van Gogh. 82 of which are believed to be true van Gogh works,
13 which are currently in dispute and 6 which are known imitations. All of
these paintings are scaled using the same technique to be equivalent sizes.

The approach for using Penn State was to gather several unquestionably van Gogh
paintings which are representative of his style (exemplar images) as a training
set. By not including negative examples in the training set the resulting
classifier is more stringent.
